The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-29 paper/paper.Rmd
shiny app part expanded in paper

- **shiny app**: An web interactive `shiny` app to customize the weight threshold. This app could be accessed [here](https://ebsmonash.shinyapps.io/yowie_app/).

>>>>

- **shiny app**: An interactive `shiny` web app to visualise the effect of selecting different weight threshold for substituting the wages data to its predicted value from a fit of the robust linear regression model. This app could be accessed [here](https://ebsmonash.shinyapps.io/yowie_app/) with the source code provided [here](https://github.com/numbats/yowie/tree/master/app).
